Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added future works

\section{Future Work}
\label{sec:future}

>>>>

\section{Future Work}
\label{sec:future}
The first aspect that we would like to focus on in the future had we had more time would be the interactions between Mississippi and its surrounding states. It is probable that in the event of a state wide evacuation, the transportation system would need to support not just the citizens of Mississippi but also those of Louisiana and Alabama.
\newline
In addition to this, we would like to do more robustness testing by generating random hurricanes and their trajectories, and plan accordingly. This would allow us to test on a much bigger data sample than the one we were able to get our hands on.
\newline
Another area that we would have liked to improve has to do with the fact that we did not take into account the trajectory of the hurricanes after they made landfall. We considered that by that time, the populations of the counties affected should have been evacuated according to the level of emergency that we assigned them.\newline
Overall, all of these would be achievable with the state of our models, but would require a lot of time to polish as it would add a significant amount of complexity to the simulations.
